PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd
added sum score and differences between case/control

**ADD SCORING FOR NEURO MEASURES**

>>>>

**ADD SCORING FOR NEURO MEASURES**
# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

```

```{ALSfrs row sums r}
dat.raw <- dat.raw %>%
  mutate(als.sum.score =
  rowSums(select(.,als.col.names), na.rm = F)
   )
```

```{ALSfrs frequencies r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(als.sum.score)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, als.sum.score) %>%
  mutate(Prop = round(n/sum(n), 2))

```
# ESS
```{ESS col names r}
ess.col.names <- dat.raw %>%
  select(
    starts_with("ess") & ends_with("numeric")
  ) %>%
  colnames()

```

```{ESS row sums r}
dat.raw <- dat.raw %>%
  mutate(ess.col.names =
   rowSums(select(.,ess.col.names), na.rm = F)
   )
```

```{ESS frequencies r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.col.names)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.col.names) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r nmsw col names}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

```

```{r scoring NMSW}
dat.raw <- dat.raw %>% 
  mutate(nmsw.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )

```

## CFS

```{r}
cfs.col.names <- dat.raw %>%
  select(
    starts_with("cfs") & ends_with("numeric")
  ) %>%
  colnames()
cfs.col.names
```
```{r}
dat.raw <- dat.raw %>%
  mutate(cfs.sum_score =
   rowSums(select(.,cfs.col.names), na.rm = F) - 11
   )
cfs.col.names.physio <- cfs.col.names[1:7]

dat.raw <- dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_physical=
   rowSums(select(.,cfs.col.names.physio), na.rm = F) - 7
   )

cfs.col.names.psych <- cfs.col.names[8:11]

dat.raw <- dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_psyhchological =
   rowSums(select(.,cfs.col.names.psych), na.rm = F) -4
   )
```

```{r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(cfs.sum_score)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  summarise(mean_total = mean(cfs.sum_score, na.rm = TRUE),
            mean_physical = mean(cfs.sum_score_physical, na.rm = TRUE),
            mean_psychological = mean (cfs.sum_score_psyhchological, na.rm = TRUE))

```

```{r}
dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_case = if_else(cfs.sum_score > 11, "Fatigue", "No fatigue")) #not sure if 11 is the right cut off

```

```{r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(cfs.sum_score_case)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
  mutate(Prop = round(n/sum(n), 2))
```
